Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-09-10 prop_letter.tex
prop_letter.tex \section{Intervals of Uncertainty} Updating...

\noindent Intuitively the expectation value of an observable relative
to a QIVPM $\bar{\mu}$ lies between two possible outcomes, which
themselves lie between the minimum and maximum bounds of the
probability intervals associated with each state~$\rho$ that is
consistent with $\bar{\mu}$ on every projector in the spectral
decomposition of the observable. If $\bar{\mu}$ is a conventional
(Born) probability measure induced by a state $\rho$, then
$\coreBorn\left(\bar{\mu},\events'\right)$ will contain the singleton
state $\rho$ and the interval collapses to a point, thus
reducing the definition to that of
Eq.~(\ref{eq:quantum-expectation}). We also note that, when restricted
to commuting projectors, the definition above is consistent with the
classical notion of the \emph{Choquet
  integral}~\cite{GilboaSchmeidler1994,Grabisch2016} which is used to
calculate the expectation value of random variables as a weighted
average.

For example, we can extend one of the fragments of valid probability
measures~$\mu_{1}$ defined in Sec.~\ref{sec:fuzzy} to a QIVPM~$\bar{\mu}_{3}$:
$\bar{\mu}_{3}(\proj{0})=\left[0.5,0.5\right]$, $\bar{\mu}_{3}(\proj{1})=\left[0.5,0.5\right]$,
and $\bar{\mu}_{3}(\proj{2})=\left[0,0\right]$. For the same observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
the Born rule probability~$\mu_{\rho}^{\mathrm{B}}$ of any state~$\rho$
consistent with $\bar{\mu}_{3}$ on $\proj{0}$, $\proj{1}$, and
$\proj{2}$ must be $\mu_{1}$. Therefore, the expectation value~$\expval{\mathbf{O}}_{\bar{\mu}_{3}}=\left[\expval{\mathbf{O}}_{\mu_{1}},\expval{\mathbf{O}}_{\mu_{1}}\right]=\left[1.5,1.5\right]$
which is an interval, but not between $0$ and $1$ because it is
not a probability of an event.

>>>>

\noindent Intuitively the expectation value of an observable relative
to a QIVPM $\bar{\mu}$ lies between two possible outcomes, which
themselves lie between the minimum and maximum bounds of the
probability intervals associated with each state~$\rho$ that is
consistent with $\bar{\mu}$ on every projector in the spectral
decomposition of the observable. If $\bar{\mu}$ is a conventional
(Born) probability measure induced by a state $\rho$, then
the Born rule probability induced by every state in
$\coreBorn\left(\bar{\mu},\events'\right)$ will be
$\mu_{\rho}^{\mathrm{B}}$ and the interval collapses to a point, thus
reducing the definition to that of
Eq.~(\ref{eq:quantum-expectation}).
For example, we can extend one of the fragments of valid probability
measures~$\mu_{1}$ defined in Sec.~\ref{sec:fuzzy} to a QIVPM~$\bar{\mu}_{3}$:
$\bar{\mu}_{3}(\proj{0})=\left[0.5,0.5\right]$, $\bar{\mu}_{3}(\proj{1})=\left[0.5,0.5\right]$,
and $\bar{\mu}_{3}(\proj{2})=\left[0,0\right]$. For the same observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
the Born rule probability~$\mu_{\rho}^{\mathrm{B}}$ of any state~$\rho$
consistent with $\bar{\mu}_{3}$ on $\proj{0}$, $\proj{1}$, and
$\proj{2}$ must be $\mu_{1}$. Therefore, the expectation value~$\expval{\mathbf{O}}_{\bar{\mu}_{3}}=\left[\expval{\mathbf{O}}_{\mu_{1}},\expval{\mathbf{O}}_{\mu_{1}}\right]=\left[1.5,1.5\right]$
which is an interval, but not between $0$ and $1$ because it is
not a probability of an event. We also note that, when restricted
to commuting projectors, the definition above is consistent with the
classical notion of the \emph{Choquet
  integral}~\cite{GilboaSchmeidler1994,Grabisch2016} which is used to
calculate the expectation value of random variables as a weighted
average.
